Visualisation of Brain Statistics with R-packages \emph{ggseg} and \emph{ggseg3d}

### 2020-04-06 README.Rmd
cant get binder to work

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/Athanasiamo/ggsegpaper/master?urlpath=rstudio)
<!-- badges: end -->

>>>>

<!-- badges: start -->
<!-- [![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/Athanasiamo/ggsegpaper/master?urlpath=rstudio) -->
<!-- badges: end -->
